---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# geeks

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/geeks)](https://CRAN.R-project.org/package=geeks)
<!-- badges: end -->

The purpose of **geeks** is to download data from three game-related geek
sites: [boardgamegeek](https://www.boardgamegeek.com),
[rpggeek](https://rpggeek.com) and [videogamegeek](https://videogamegeek.com).

At the moment, the usage covers fetching and parsing game entries, plays
and families. Support for collections, search and threads is planned.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jchrom/geeks")
```

## Example

The following snippet retrieves data about a set of games, and coerces them
into a data frame:

```{r}
library(geeks)
get_games(c(174430, 161936, 224517))
```

Play data can be obtained given a game id:

```{r}
get_plays(174430)
```

Multiple families can be obtained at once:

```{r}
get_families(c(7544, 17634))
```

## Built on

[xml2](https://github.com/r-lib/xml2),
[httr](https://github.com/r-lib/httr),
[tibble](https://github.com/tidyverse/tibble) and
the BGG [API2 docs](https://boardgamegeek.com/wiki/page/BGG_XML_API2).
