---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# geeks

<!-- badges: start -->
<!-- badges: end -->

The purpose of **geeks** is to download data from three game-related geek
sites: [boardgamegeek](https://www.boardgamegeek.com),
[rpggeek](https://rpggeek.com) and [videogamegeek](https://videogamegeek.com).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jchrom/geeks")
```
## Example

At the moment, fetching and parsing most of game data is implemented. Other
components such as plays, threads and search are to be added later.

The following snippet retrieves data about a set of games, and coerces them
into a data frame:

```{r example}
library(geeks)

games = get_game(c("174430", "161936", "224517"), domain = "boardgame")

game_info(games)

game_stats(games)
```

## Built on

Credits mostly to [xml2](https://github.com/r-lib/xml2),
[httr](https://github.com/r-lib/httr)
and the BGG [API2 docs](https://boardgamegeek.com/wiki/page/BGG_XML_API2).
